When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-06 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
included h3a and h3b plots

The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of $n$-back level (`r apa_print(hypothesis3b_model)$full_result$level`, `r apa_print(hypothesis3b_BF_levels)$statistic$level`) and an interaction between $n$-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian`).
Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median.
Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of $n$-back levels (**Supplement**).

>>>>

```{r h3a-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Difference scores for subjective values when subtracting 2- from 1-back and 3- from 2-back. Each line indicates a participant, the colours indicate their Need for Cognition score. $N=116$.", fig.pos="H"}

  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3a-plot.png"))

The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of $n$-back level (`r apa_print(hypothesis3b_model)$full_result$level`, `r apa_print(hypothesis3b_BF_levels)$statistic$level`) and an interaction between $n$-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian`).
Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median.
Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of $n$-back levels (Figure\ \@ref(fig:h3b-plot)).

INSERT FIGURE 5 HERE

```{r h3b-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="NASA-TLX sum scores for each $n$-back level. Colours indicate Need for Cognition (NFC) score above or below the median. $N=116$.", fig.pos="H"}

  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3b-plot.png"))
